An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-21 EconGrowth.Rnw
Beginning the work on the lattice version of the triangle plot that contains (a) all the relevant energy parameters and their confidence intervals (on the y axis) and (b) the values of the parameters (on the x axis).
Edited the to-do list in the paper.

\item{Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel. But, wait until we know if we have symmetric confidence intervals before doing this. These graphs won't work if we have asymmetric CIs.}

@@

\item \st{Reese: Add text from Word verson of paper to the LaTeX version.}

@@

<<Test, eval=TRUE>>=
CIvsParamDF(model="CESe", param="sigma", energyType="Q")
CIvsParamPlot(model="CESe", param="sigma", energyType="Q")

@

@@

>>>>

@@

\item{\st{Reese: Add text from Word verson of paper to the LaTeX version.}}
\item{\st{Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel. But, wait until we know if we have symmetric confidence intervals before doing this. These graphs won't work if we have asymmetric CIs.}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Confidence Intervals for Cobb-Douglas and CES Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$. When the 95\% confidence interval for $\gamma$ and $\delta$ extends to 0.0 and 1.0, respectively, we cannot say whether including energy in the production function is helpful. If the value of $\gamma$ is close to 0.0, and the 95\% confidence interval does not extend to 0.0, we know that energy does not play an important role in producing economic output for the Cobb-Douglas model. If the value of $\delta$ is close to 1.0 and the 95\% confidence intervale does not extend to 1.0, we know that energy does not play an important role in producing economic output for the CES model.

The following figure shows these relationships.

<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval width vs. parameter value for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.">>=
CIvsParamLattice(countryAbbrevScaling=0.6)
@
